Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated Paper
Similarity reduced on introduction and conclusion.
Updated similarity
Work in progress.
Updated Proposal
Work in progress.

    Biologically inspired algorithms have proven to be very effective when
    solving complex optimization problems
    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
    the more challenging the problem, the more computing power it will require
    to solve them \cite{ontiveros2018high}. One technique to manage this
    processing power is to use distributed computing
    \cite{thain2005distributed} or the cloud available resources to help solve
    the problem \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
    allows adaptation of the computing power according to the problem's
    complexity.

@@

    Our inspiration for this algorithm was found in the study and observation of
    nature, using general abstraction to identify what most animal species have in
    common: the life cycle. We present an algorithm inspired by the biological
    life-cycle of animal species, which consists of several stages
    \cite{read1968system}: birth, growth, reproduction, and death. The combination
    of those processes results in evolution. As in nature, we intend to execute all
    these stages in parallel and asynchronously on a constantly evolving
    population.

@@

        This algorithm seeks to imitate the natural life cycle, where new individuals
        are born at any moment and mature over time, where they age and then suffer
        mutations throughout their lives. In reproduction, couples match by mutual
        attraction. Death can happen to everyone: from a newborn to an aged adult,
        where the individual's fitness will impact their longevity. We display the
        general model concept in Figure~\ref{fig.algorithm_model}.

>>>>

    Biologically inspired algorithms have proven to be very effective when
    solving complex optimization problems
    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
    the more challenging the problem, the more computing power it will require
    to solve them \cite{ontiveros2018high}. One technique to manage this
    processing power is to use distributed computing
    \cite{thain2005distributed} or the cloud available resources to help solve
    the problem \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
    allows adaptating the required computing power according to the problem's
    complexity.

@@

    In previous work, we presented an algorithm inspired by nature, where we
    used observation, analysis, and abstraction to model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes results in evolution. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

@@

        Our algorithm's goal is to mimic the animal life cycle, where at any
        given moment, new individuals are born to be part of the population and
        participate in the collective evolution. As time passes, they grow
        older and mature, suffering changes throughout their lives that we
        chose to represent as mutations. In our analysis, we considered a
        couple's attraction a fundamental factor in reproduction. We thought of
        death's work to maintain balance in the population by enforcing the
        survival of the fittest. As in life, death can happen to everyone: from
        a newborn to the elderly, where fitness will determine the individual's
        longevity. We display the general model concept in
        Figure~\ref{fig.algorithm_model}.
